---
title: "REtable"
output: html_document
date: "2022-10-11"
---

The following table presents data sourced from Zillow about rental costs and home prices. 
I am a real estate investor and I'd like to use the table to identify areas with high CapRates (rent/home price).




```{r RE}
library(dplyr)
library(tigris)
library(plotly)
library(rjson)
library(knitr)
library(kableExtra)
library(sparkline)
library(shiny)
library(reactable)
library(reactablefmtr)
library(remotes)
library(dataui)
#this data is from www.zillow.com/Data
two_bedroom_data<-read.csv("/Users/francesco/Downloads/Viz/City_zhvi_bdrmcnt_2_uc_sfrcondo_tier_0.33_0.67_sm_sa_month.csv")
rent_data<-read.csv("/Users/francesco/Downloads/Viz/City_zori_sm_month.csv")
taxes<-read.csv("/Users/francesco/Downloads/Viz/Taxes.csv")
url <- 'https://raw.githubusercontent.com/plotly/datasets/master/geojson-counties-fips.json'
counties <- rjson::fromJSON(file=url)
taxes$State = state.abb[match(taxes$State,state.name)]
capRate<-rep(NA,nrow(rent_data))
tax<-rep(NA,nrow(rent_data))
fips<-rep(NA,nrow(rent_data))
rent_trend<-matrix(NA,nrow(rent_data),60)
own_trend<-matrix(NA,nrow(rent_data),60)
price<-rep(NA,nrow(rent_data))

```
Here I have calculated the CapRates and adjusted for the property tax. 
```{r}
for (i in 1:nrow(two_bedroom_data)) {
  fips_str = lookup_code(two_bedroom_data$State[i],two_bedroom_data$CountyName[i])
  fips_state = substr(fips_str,unlist(gregexpr('\'', fips_str))[1]+1,unlist(gregexpr('\'', fips_str))[2]-1)
  fips_county = substr(fips_str,nchar(fips_str)-4,nchar(fips_str)-2)
  fips_dense = paste(fips_state,fips_county,sep="")
  two_bedroom_data$Metro[i] = substr(fips_dense,1,3)
}

for (i in 1:nrow(rent_data)) {
  fips_str = lookup_code(rent_data$State[i],rent_data$CountyName[i])
  fips_state = substr(fips_str,unlist(gregexpr('\'', fips_str))[1]+1,unlist(gregexpr('\'', fips_str))[2]-1)
  fips_county = substr(fips_str,nchar(fips_str)-4,nchar(fips_str)-2)
  fips_dense = paste(fips_state,fips_county,sep="")
  fips[i] = fips_dense
  rent_trend[i,] = as.numeric(rent_data[i,39:98])
  rent=rent_trend[i,ncol(rent_trend)]
  if(rent_data$RegionID[i] %in% two_bedroom_data$RegionID){
    own_trend[i,] = as.numeric(two_bedroom_data[two_bedroom_data$RegionID==rent_data$RegionID[i],221:280])
    own = own_trend[i,60]
  }
  else {
    df.metro = two_bedroom_data[two_bedroom_data$Metro==substr(fips_dense,1,3),]
    if(nrow(df.metro)>=1){
      own = df.metro[1,ncol(df.metro)]
    }
    else{
      own = mean(two_bedroom_data[two_bedroom_data$State==rent_data$State[i],ncol(two_bedroom_data)])
    }
  }
  
  tax[i] =as.numeric(substr(taxes[taxes$State==rent_data$State[i],2][2],1,4))/100*own
  capRate[i] = (rent*12- tax[i]) / own 
  price[i] = own
}
```

This table shows the CapRate for each city. I listing the price helps me target properties within my ideal price range. NJ is excluded because it has increased property tax on landlords and Florida is exlucded due to high insurance costs.
```{r}
df.table <-data.frame(City = rent_data$RegionName, State=rent_data$State,Price=price,CapRate=capRate,Tax=tax) 

df.table = df.table %>% filter(Price>107000,Price<480000,State!="NJ",State!="FL",CapRate>.09)

table<-df.table%>%reactable(columns = list(City= colDef(name="City"),State=colDef(name="State"),CapRate=colDef(name = "CapRate",format=colFormat(digits=2)),Tax=colDef(name = "Property Tax",format=colFormat(digits = 0))),defaultSorted = "CapRate",defaultSortOrder = "desc") 
table
```



